\bf On Devon Allen's Disqualification at the 2022 World Track and Field Championships

### 2024-06-20 Manuscript/manuscript.tex
added explanation of why 0.1 sec reaction barrier

Devon Allen, an alumnus of the University of Oregon in Eugene, Oregon, was
expected to be a contender for the 2022 World Track and Field Championships 110 
meter hurdle. After running the event in 12.84 seconds in early June 2022 
(only 0.04 seconds away from the world record \citep{wa2022preview}) and coming 
in third at the United States Track and Field Championships also in Eugene 
in late June, Allen was poised to compete in the 2022 World Track and 
Field Championships in August, which would also be held in Eugene, Oregon.
At the World Championships, Allen made it through the preliminary
heats and semifinals to reach the final heat while posting reaction times of 
0.123 and 0.101 in his preliminary heat and semifinal, respectively. 
His disqualification in the final heat by reacting in 0.099 seconds, just 0.001
seconds faster than the 0.1 threshold set by the International Association of
Athletics Federations (IAAF), was met
with shock from both Allen and fans alike. NBC, who was broadcasting the
championships in the United States, later uploaded a video to their YouTube
channel that showed the disqualification
(\url{https://www.youtube.com/watch?v=D6NXTMo-1yM}).
The crowd erupted with jeers
when they realized that Allen was disqualified, angry at the result. Had Allen 
reacted just 0.001 seconds slower he would have been allowed to compete.

>>>>

Devon Allen, an alumnus of the University of Oregon in Eugene, Oregon, was
expected to be a contender for the 2022 World Track and Field Championships 110 
meter hurdle. After running the event in 12.84 seconds in early June 2022 
(only 0.04 seconds away from the world record \citep{wa2022preview}) and coming 
in third at the United States Track and Field Championships also in Eugene 
in late June, Allen was poised to compete in the 2022 World Track and 
Field Championships in August, which would also be held in Eugene, Oregon.
At the World Championships, Allen made it through the preliminary
heats and semifinals to reach the final heat while posting reaction times of 
0.123 and 0.101 in his preliminary heat and semifinal, respectively.  The
reaction time barrier for all sprint related events is 0.1 seconds as set by the
International Association of Athletics Federation (IAAF) and is meant
to prevent athletes from trying to predict the starting gun.
His disqualification in the final heat by reacting in 0.099 seconds, just 0.001
seconds faster than the 0.1 threshold, was met
with shock from both Allen and fans alike. NBC, who was broadcasting the
championships in the United States, later uploaded a video to their YouTube
channel that showed the disqualification
(\url{https://www.youtube.com/watch?v=D6NXTMo-1yM}).
The crowd erupted with jeers
when they realized that Allen was disqualified, angry at the result. Had Allen 
reacted just 0.001 seconds slower he would have been allowed to compete.
